\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}

% Core packages
\usepackage{amsmath,amssymb}
\usepackage{tikz-cd}
\usepackage{multicol}
\usepackage{array}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage[hidelinks]{hyperref}

% Paragraphs
\setlength{\parindent}{0pt}
\setlength{\parskip}{1\baselineskip}

\title{Project Proposal: SinChat - Real-time Client-Server Chat Application}
\author{Network Programming Course}
\date{\today}

\begin{document}
\maketitle

\section{Group Information}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.26\textwidth} >{\raggedright\arraybackslash}p{0.20\textwidth} >{\raggedright\arraybackslash}p{0.28\textwidth}}
\toprule
\textbf{Name} & \textbf{Student ID} & \textbf{GitHub Account ID} \\
\midrule
Member 1 Name & Student ID 1 & \href{https://github.com/username1}{username1} \\
Member 2 Name & Student ID 2 & \href{https://github.com/username2}{username2} \\
Member 3 Name & Student ID 3 & \href{https://github.com/username3}{username3} \\
Member 4 Name & Student ID 4 & \href{https://github.com/username4}{username4} \\
Member 5 Name & Student ID 5 & \href{https://github.com/username5}{username5} \\
Member 6 Name & Student ID 6 & \href{https://github.com/username6}{username6} \\
\bottomrule
\end{longtable}

\textbf{GitHub Repository:} \url{https://github.com/ThaiDevv/sinchat-network-programming}

\section{Project Overview}

Our team proposes to build \textbf{SinChat}, a Real-time Client-Server Chat Application related to Network Programming. The project will allow users on different devices to communicate directly through a centralized backend using a stateful TCP socket protocol. The client will feature a modern, dark-themed JavaFX desktop graphical user interface, allowing users to register, log in, manage conversations, upload avatars, and send real-time messages.

The main goal of this project is to apply network programming concepts such as TCP socket programming, newline-delimited JSON message framing, request-response correlation, client-server coordination, multithreading, concurrent data structures, connection pooling, and secure authentication handling.

\section{What We Want to Do}

We want to create a full-stack, desktop-based chat application that supports real-time text messaging between multiple users. The system uses a centralized Java backend with a TCP server for authentication, profile management, conversation queries, message sending, and real-time events such as new messages and typing indicators.

The project will emphasize robust network architecture by implementing a custom TCP router. Each client sends JSON actions over one socket connection, and the server dispatches those actions to the correct handler before returning JSON responses or pushing real-time events back to connected users.

\section{Main Features}

The features our team plans to add and complete are based directly on our source code architecture:

\begin{itemize}
    \item \textbf{User Authentication:} Secure registration, login, and a forgot-password flow with generated reset codes. Passwords are cryptographically hashed using BCrypt.
    \item \textbf{Real-time Messaging:} Instant message delivery through the TCP socket without needing to poll the server.
    \item \textbf{Private Conversations:} 1-on-1 private chats between users with synchronized message history retrieved through TCP actions.
    \item \textbf{Typing Indicators:} Real-time visual feedback when another user is typing, implemented via throttled TCP broadcasts.
    \item \textbf{Avatar Updates:} Ability for users to change their profile avatars by sending avatar data through the TCP client flow.
    \item \textbf{Async Network Layer:} Non-blocking asynchronous API calls on the client side using \texttt{CompletableFuture} to maintain a responsive GUI.
    \item \textbf{Robust Security \& Error Handling:} Path traversal protection for file serving, CORS preflight handling, strict parameter validation, and SQL injection prevention via Prepared Statements.
\end{itemize}

\section{Technology Stack}

Our team plans to use the following stack for the project:

\begin{itemize}
    \item \textbf{Programming Language:} Java 21 (LTS) for both Client and Server
    \item \textbf{Client GUI Framework:} JavaFX 21
    \item \textbf{Server Architecture:} Java \texttt{ServerSocket} and per-client connection handlers
    \item \textbf{Network Protocol:} Stateful TCP sockets using newline-delimited JSON actions
    \item \textbf{Database:} MySQL 8.x with \texttt{HikariCP} for high-performance connection pooling
    \item \textbf{Data Format \& Security:} JSON parsing via \texttt{Gson}; password hashing via \texttt{jBCrypt}
    \item \textbf{Deployment:} Multi-stage Docker containerization and Render cloud hosting
    \item \textbf{Testing Tools:} JUnit 5 and Mockito for TCP action integration and service layer testing
\end{itemize}

\section{Expected Final Achievement}

At the end of the project, our team expects to deliver a robust, production-ready client-server chat application. The JavaFX desktop client will feature a polished, user-friendly interface that updates instantly without refreshing. The server will demonstrate efficient handling of continuous TCP socket connections, request-response messages, and server-pushed chat events.

The final product will show that our team understands how to design, implement, and deploy a complete network programming system using sockets, connection pools, and a clear JSON action protocol. We will also provide full source code, comprehensive Markdown documentation, Docker setup instructions, and integration tests in the GitHub repository.

\section{Project Planning}

Each phase lasts two weeks. The following plan shows what our team should complete in each phase.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.18\textwidth} >{\raggedright\arraybackslash}p{0.72\textwidth}}
\toprule
\textbf{Phase} & \textbf{Tasks to Complete} \\
\midrule
Phase 1: Weeks 1--2 & Finalize project topic, create GitHub repository, design system architecture, set up Maven project structures for Client and Server, and prepare initial JavaFX UI wireframes. \\
\midrule
Phase 2: Weeks 3--4 & Design MySQL database schema, implement HikariCP connection pooling, build TCP actions for user authentication (Login/Register), and integrate BCrypt hashing. \\
\midrule
Phase 3: Weeks 5--6 & Implement the TCP server and client wrapper, establish connection lifecycle (connect/join/disconnect), and develop the JavaFX chat view layout. \\
\midrule
Phase 4: Weeks 7--8 & Complete real-time message broadcasting, implement TCP actions for fetching conversation history, and add typing indicators with client-side throttling. \\
\midrule
Phase 5: Weeks 9--10 & Implement avatar update flow, harden validation and error handling, write integration tests with Mockito, and refine the dark-themed UI. \\
\midrule
Phase 6: Weeks 11--12 & Final testing, create multi-stage Dockerfile, deploy to Render, write comprehensive documentation, clean GitHub repository, and prepare final presentation. \\
\bottomrule
\end{longtable}

\section{Team Role Distribution}

\begin{itemize}
    \item \textbf{Member 1:} Project leader, database design, connection pooling, and final report coordination.
    \item \textbf{Member 2:} TCP authentication actions, authentication logic, and request validation.
    \item \textbf{Member 3:} TCP server implementation, real-time broadcasting, and concurrent state management.
    \item \textbf{Member 4:} JavaFX desktop GUI design, theming, and layout integration.
    \item \textbf{Member 5:} Client-side TCP network layer, async tasks, and UI event binding.
    \item \textbf{Member 6:} Testing (JUnit/Mockito), Docker containerization, Render deployment, and documentation.
\end{itemize}

\section{Conclusion}

This project is suitable for the Network Programming course because it requires real communication between distributed components, TCP socket design, database connection management, multithreading, and asynchronous programming. By completing this project, our team will gain practical experience in building and deploying a complete, network-based, real-time software system from scratch.

\end{document}
